---
title: "**DATA TIDYING PRESENTATION**"
author: "Amalia Jiménez Toledano"
output: 
  revealjs::revealjs_presentation:
    theme: sky
    center: T
    self_contained: false
    highlight: kate
    transition: concave
    css: custom.css
---


```{r include=FALSE}
library(Stat2Data)
library(ggplot2)
data(Clothing)
summary(Clothing)
library(knitr)
library(plotly)
library(tidyverse)
library(prettyunits)
```

# READ THE DATA AND SUMMARY


The aim of this study is a brief explanation and representation of the `CLOTHING` database taken from the `Stat2Data` package:

<div2>**The variables of the data are the following:**</div2>

<ul>
<li class="fragment highlight-current-blue" data-fragment-index="1">**ID**: 	Case ID</li>
<li class="fragment highlight-current-red" data-fragment-index="2"> **Amount**: Net dollar amount spent by customers in their latest purchase from this retailer</li>
<li class="fragment highlight-current-green" data-fragment-index="3"> **Recency**:	Number of months since the last purchase</li>
<li class="fragment highlight-current-blue" data-fragment-index="4"> **Freq12**:	Number of purchases in the last 12 months</li>
<li class="fragment highlight-current-red" data-fragment-index="5"> **Dollar12**:	Dollar amount of purchases in the last 12 months</li>
<li class="fragment highlight-current-green" data-fragment-index="6"> **Freq24**:	Number of purchases in the last 24 month</li>
<li class="fragment highlight-current-blue" data-fragment-index="7"> **Dollar24**:	Dollar amount of purchases in the last 24 months</li>
<li class="fragment highlight-current-red" data-fragment-index="8">  **Card**:1 for customers who have a private-label credit card with the retailer, 0 if not
</li>
</ul>


## DATABASE CONSIDERATIONS


```{r include=FALSE}
Clothing <- Clothing[-60,-1] # Missing Value
Clothing$Card <- as.factor(Clothing$Card) # Categorical variable


card=matrix(0,nrow=nrow(Clothing),ncol=1)
for (i in 1:nrow(card)){
  if(Clothing[i,7]==1){
    card[i]="Private label"
  }
  if(Clothing[i,7]==0){
    card[i]="Public label"
  }
}

Clothing$Card <- as.factor(card)
```


```{r}
summary(Clothing)
```

Since the variable "Card" is categorical, the transformation is performed:

```{r}
Clothing$Card <- as.factor(Clothing$Card)
```

# CARD VARIABLE

The variable `Card` takes the following values:

<li> 1: customers who have a private-label credit card </li>
<li> 0: customers who have a public-label credit card </li>



```{r echo=FALSE}

colors <- c('rgb(211,94,96)', 'rgb(128,133,133)')

plot1 <- plot_ly(Clothing, labels = ~Card,  type = 'pie',
                 marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))
plot1 <- plot1 %>% layout(title = 'PIE  PLOT CARD VARIABLE',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

htmlwidgets::saveWidget(plot1,'plotly1.html')
knitr::include_url('plotly1.html', height = "400px")
```




<div2> It is found that 66.66$\%$ of consumers have a private-label credit card and 33.33$\%$ not.</div2>



# BOXPLOT RECENCY AND AMOUNT

<p class="fragment grow" data-fragment-index="1">Below are the `box-plots` of the *Recency* and *Amount* variables.</p>

## BOXPLOT RECENCY

```{r, echo=F, warning=FALSE}
ggplot(Clothing, aes(x=0,y=Recency))+ 
      geom_boxplot(color="black",fill="lightslateblue",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Recency", y="Recency")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```

## BOXPLOT AMOUNT

```{r, echo=F, warning=FALSE}
Clothing=Clothing[-60,]
ggplot(Clothing, aes(x=0,y=Amount))+ 
      geom_boxplot(color="black",fill="gold3",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Amount", y="Amount")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```



# REGRESSION MODEL

<div22>We are interested in knowing the relationship of the variable `Amount` with respect to the variables `Freq24` and  `Dollar24`:</div22>


## SUMMARY OF THE MODEL


```{r include=FALSE}
out <- lm(Amount ~ Freq24+Dollar24,data=Clothing)
summary(out)
library(knitr)
```

```{r echo=FALSE}
kable(summary(out)$coef, digits=3)
```



<div3>**Results:**</div3> $y_i=\beta_0+\beta_1x_1+\beta_2x_2=-22549.66-14210.5x_1+193.044x_2$

--> The variable `Dollar24`and `Freq24` are found to be significant for the model.


# DYNAMIC PLOT

<div2>Click on the dots to see the type of credit card:</div2>


```{r echo=FALSE}
plotly=plot_ly(Clothing, x = ~Freq12, y = ~Freq24, type = "scatter", mode = "markers",
        symbol = ~Card) %>% 
        layout(title = "Freq12 vs Freq 24",
               xaxis = list(title = "Freq12"), 
               yaxis = list(title = "Freq24"))
htmlwidgets::saveWidget(plotly,'plotly.html')
knitr::include_url('plotly.html', height = "400px")
```


# THANKS
